\section{Experience}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading {VMware} {Feb 2022 - Present} 
{Member of Technical Staff} {Austin, TX}
\small
\begin{justify}
\vspace{5pt}
      \resumeItemListStart
        \resumeItem{Worked on the design and development of highly distributed, and configuration driven observability, alerting and incident management platforms and SaaS services  for \textbf{VMware cloud (VMC on AWS)}.}
        \resumeItem{Developed high volume, low latency data collection and incident management pipelines providing alert standardization, enrichment, correlation, auto-remediation, and escalation serving more than \textbf{3000 Software-Defined Data Centers}.}
        \resumeItem{Implemented an offset auto-advancement feature in the \textbf{data plane} (deployed in Kubernetes cluster), by dynamically adjusting Kafka partition offsets to prioritize live data over stale during high latency in downstream services.}
        \resumeItem{Designed and implemented end-to-end testing suite for the alerting workflow within a distributed multi-tenant system, ensuring comprehensive coverage across diverse tenants and environments, resulting in a significant \textbf{30\% reduction} in critical system errors.}
        \resumeItem{Worked on the design and implementation of an alert correlation service, replacing BigPanda(Alert Correlation Engine), aimed at minimizing on-call toil by automatically grouping related alerts into single, manageable incidents for on-call engineers.}
        \resumeItem{Realized \textbf{400k monthly savings} through strategic log cost optimization by partitioning logs into indexed and non-indexed segments.}
        \resumeItem{Led the responsibilities of identifying and fixing \textbf{security} vulnerabilities for 20+ platform and SaaS services}
        \resumeItem{Managed critical \textbf{on-call} responsibilities while resolving production outages and ensuring uninterrupted service delivery.}
        \resumeItem{Developed \textbf{Python automation scripts} to import, validate and delete alerts in cloud-based alert management system.}
        \resumeItem{Led operational improvement initiatives, catalyzing a \textbf{2x surge} in ticket throughput while notably slashing Mean Time to Resolution, Mean Time to Acknowledge, and total backlog size, fostering a process-centric approach.}
\resumeItemListEnd
\vspace{5pt}
\resumeItemColon{\textit{Stack}}{\textbf{\textit{Java, Spring Boot, Python, Kafka, Kubernetes, Docker, Amazon RDS, Concourse CI}}}
% \end{itemize}
\end{justify}
\vspace{10pt}
\resumeSubheading {Infosys} {Jun 2015 - Dec 2019} 
{Senior System Engineer(Java Backend)} {Pune, MH}
\small
\begin{justify}
\vspace{5pt}
% \begin{itemize}
      \resumeItemListStart
        \resumeItem{Implemented a web-based solution using Spring Boot that enabled the automation of the “Know Your Customer” (KYC) process of \textbf{more than 2000 corporate clients}.}
        % \resumeItem {Fixed an issue in notification microservice, by improving the design to log the entity id's which \textbf {reduced the failed use cases by 80\%.}}
   
        \resumeItem{Developed a web-based solution that enables the automation of DB deployment with backup, validation and rollback functionalities which reduced time of deployment from 48 hours  to almost instantaneous and removed human dependency. }
        \resumeItem{Implemented automated bots to perform searches on the office of Foreign Asset Control, Fraud and Abuse Control Information System, Food and Drug Administration, Office of Inspector General, and several other websites facilitating faster \textbf{(90\% reduction)} background verification.}
        %\resumeItem{Designed a Client-facing Status update portal to bring transparency to engagement by providing \textbf{real-time engagement status} to the client.}
        
       %\resumeItem {Improved the logging module of notification microservice, by enhancing the design which \textbf {reduced the failed use cases by 80\%.}}
        % \resumeItem{Modified App service, API service and data layer to add embedded resources to the API. Used inline queries and stored procedures.}
        % \resumeItem {Modified App service, API service to enhance a feature. Added embedded resource to media plan API to respond with JSON that contain media plan details.}
        %\resumeItem {Scaled the application, enabling RabbitMQ, while achieving asynchronous execution of tasks.}
        \resumeItem {Responsible for creating the design documents and unit tests with test plans and test cases for developed features.}
        \resumeItem{Played a pivotal role in resource allocation, task delegation, and mentoring team members to foster their professional growth and development.}
\resumeItemListEnd
% \end{itemize}
\end{justify}
\vspace{5pt}
\resumeItemColon{\textit{Stack}}{\textbf{\textit{Java, Selenium, .NET, PostgreSQL, Spring Boot, JUnit}}}

\resumeSubHeadingListEnd
\vspace{-12pt}